A sustainable approach to tourist signage on (historical) trails

### 2023-07-17 paper.tex
Avanzamento

We first check the above strategies against the Universal Design Principles \cite{udi97a}:

\begin{enumerate}
	\item Equitable Use
	\item Flexibility in Use
	\item Simple and Intuitive
	\item Perceptible Information
	\item Tolerance for Error
	\item Low Physical Effort
	\item Size and Space for Approach and Use
\end{enumerate}

The labels are self-descriptive, and we address the reader to the discussion in the referenced document for a more detailed explanation.

Such minimalistic solutions (se figure \ref{fig:qrnfccoin}) compares surprisingly well when compared with other solutions that make use of the user's smartphone. There is a trade-off concerning capacity, but in many circumstances a capacity of 2-300 words is sufficient to convey the description of the site, or provide directions for the the visit. In exchange, a solution besed on NFC or QR-codes:
\begin{itemize} 
\item does not require any power supply
\item is easy to use
\item has a limited impact on the landscape
\item is not exposed to theft
\item has a negligible cost
\item is durable
\item produces a limited quantity of waste when disposed
\item is readable at a moderate distance, a feature that differentiates NFP and QR-codes
\item can be read aloud or translated
\item can be stored by the user's device.
\end{itemize}

Checking passive devices solutions against the Universal Design principles, we assess their accessibility.

\begin{itemize}
	\item {\em Equitable use} is tighly related to the smartphone technology, which is itself considered a vehicle for equitability,
	\item {\em Flexibility in use} is allowed by the computing capabilities of the device, which allows to listen to the info instead or reading, or translate the information in a different language,
	\item {\em Simple and intuitive use} holds since the operation requires an application, possibly already installed since useful in many occasions, and tag reading requires
	\item{\em Perceptible information} is a critical requirement, which contrast with the aim of keeping low the environmental intrusion. This point will be further discussed in the section devoted to the implementation
	\item{\em Tolerance for error}: there are no margins to use the device in a way that comprimizes user safety. The deliberate or accidental release of the passive device into the environment determines a minor pollution
	\item{\em Low physical effort} holds, although the user needs to carry the smartphone
	\item{Size and Space for approach and use} have to be carefully considered, since in the case of the NFC the smartphone need to be almost in touch with the passive device, while the QR-code must be in line of sight and frameable without effort
\end{itemize}

It significantly outperforms any active device, except for the capacity, and the NFC compares favorably only when capacity and size are prominent.

>>>>

A preliminary check verifies compliance with the Universal Design Principles \cite{udi97a}:

%\begin{enumerate}
%	\item Equitable Use
%	\item Flexibility in Use
%	\item Simple and Intuitive
%	\item Perceptible Information
%	\item Tolerance for Error
%	\item Low Physical Effort
%	\item Size and Space for Approach and Use
%\end{enumerate}

%The labels are self-descriptive, and we address the reader to the discussion in the referenced document for a more detailed explanation.
%Checking passive devices solutions against the Universal Design principles, we assess their accessibility.

\begin{itemize}
	\item {\em Equitable use} is tighly related to the smartphone technology, which is itself considered a vehicle for equitability,
	\item {\em Flexibility in use} is enabled by the computing capabilities of the device, which allows to listen to the info instead or reading, or translate the information in a different language,
	\item {\em Simple and intuitive use} holds since the operation requires a single application, possibly already installed since useful in many circumstances, and tag reading requires a single touch
	\item{\em Perceptible information} is a critical requirement, which contrasts with the aim of keeping low the environmental intrusion. This point will be further discussed in the section devoted to the implementation
	\item{\em Tolerance for error}: there are no margins to use the device in a way that compromises user safety. The deliberate or accidental release of the passive device into the environment determines a minor pollution
	\item{\em Low physical effort} holds, although the user needs to carry the smartphone
	\item{Size and Space for approach and use} have to be carefully considered. In the case of the NFC the smartphone needs to be nearly in touch with the passive device, while the QR-code must be in line of sight and frameable without effort
\end{itemize}

Such a minimalistic solutions (se figure \ref{fig:qrnfccoin}) compares well compared with other solutions that make use of the user's smartphone. There is a trade-off concerning capacity, but in many circumstances a capacity of 2-300 words is sufficient to convey the description of the site, or provide directions for the the visit. If capacity is not an issue a solution based on NFC or QR-codes exhibits a number of advantages:
\begin{itemize} 
\item does not require any power supply
\item has a limited impact on the landscape
\item is not exposed to theft
\item has a negligible cost
\item is durable
\item produces a limited quantity of waste when disposed
\item the content can be stored by the user's device for successive utilization
\end{itemize}

%It significantly outperforms any active device, except for the capacity, and the NFC compares favorably only when capacity and size are prominent.

A solution based on the user smartphone associated with passive devices compares favorably with traditional signage boards. Considering the limits of the latter approach listed in table \ref{tab:board}:

%The adoption of passive devices compares favorably with traditional boards, considering the strengths and limits as listed above.

\begin{itemize}
	\item dimensions: a 2-300 characters QR-code has a dimension in the order of 100 $cm^2$
	\item logistics: QR-code board can be installed on any sort of pre-existent or natural support
	\item impact: the board has a minimal interference with the landscape and may easely go un-noticed if not properly advertised
	\item accessibility for the visually impaired: the text can be read aloud
	\item international: the text can be translated
	\item update: the board can be easely replaced when the content becomes obsolete
	\item disposal: the card releases a limited quantity of pollutants related with ink support (paper or plastic)
\end{itemize}

%One of the issues the host must resolve is the availability of support for electronic devices. The provisioon of such support has a footprint that ha		
%may be present, but, in the spirit of our investigation, power supply should be address renewable sources, like wind, sunlight and similar.
%One option discriminates the use of an electronic device on the side of the user. 
%In case we assume the user does not have a electronic device with her, the 
%One option is to introduce active electronics: the touristic site administration provides a

There are two relevant trade-offs that the host needs to resolve. One is related with the visibility of the tag. The trade-off is among the
